GiftGiver: The Gift Recommender \\ {\small AAI -- Instructor: Prof. Jane Hsu}

### 2011-06-22 paper/paper.tex
another change

\begin{tikzpicture}
    \begin{axis}[x tick label style={/pgf/number format/1000 sep=}, ylabel=Weight, enlargelimits=0.15, legend style={at={(0.5, -0.15)}, anchor=north, legend columns=2}, ybar, bar width=7pt]
    \addplot coordinates {(1, 4.583)};
    \addplot coordinates {(2, 4.917)};
    \addplot coordinates {(3, 4)};
    \addplot coordinates {(4, 4.06)};
    \addplot coordinates {(5, 4.31)};
    \addplot coordinates {(6, 3.75)};
    \addplot coordinates {(7, 4.583)};
    \addplot coordinates {(8, 2.75)};
    \addplot coordinates {(9, 4.25)};
    \addplot coordinates {(10, 2.583)};
    \addplot coordinates {(11, 2.583)};
    \addplot coordinates {(12, 1.583)};
    \legend{Occasion,Relationship,Price,Date,Interests,Receiver's Career,Receiver's Gender,Receiver's Religion,Receiver's Age,Sender's Career,Sender's Gender,Sender's Religion}
    \end{axis}
\end{tikzpicture}

@@

Briefly explain our algorithms

\subsubsection{Feature Vectors}
As a recommendation system, we use a feature matching type of the recommendation system[韋狄再common sense報過的那邊survey paper].
We analyze 60 gifts items and 3 common occasions by 8 features.  
The features are:
1.[ Practical   ] – Is it functional or just for decoration?
2.[ Meaningful  ] – Is it has other meaning besides its function? 
3.[Beautiful    ] – Is it good looking?
4.[Trendy       ] – Is it fashion?
5.[Impersonal   ] – Is it just for him/her or other people can use it?
6.[Romantic ] – Is it present for love and sweet?
7.[Geeky        ] – Is it electrical?
8.[Fun      ] – Is it let you happy in a pure way?

>>>>

\begin{tikzpicture}
    \begin{axis}[x tick label style={/pgf/number format/1000 sep=}, ylabel=Weight, legend style={at={(0.5, -0.15)}, anchor=north, legend columns=2}, ybar, bar width=7pt]
    \addplot coordinates {(1, 4.583)};
    \addplot coordinates {(2, 4.917)};
    \addplot coordinates {(3, 4)};
    \addplot coordinates {(4, 4.06)};
    \addplot coordinates {(5, 4.31)};
    \addplot coordinates {(6, 3.75)};
    \addplot coordinates {(7, 4.583)};
    \addplot coordinates {(8, 2.75)};
    \addplot coordinates {(9, 4.25)};
    \addplot coordinates {(10, 2.583)};
    \addplot coordinates {(11, 2.583)};
    \addplot coordinates {(12, 1.583)};
    \legend{Occasion,Relationship,Price,Date,Interests,Receiver's Career,Receiver's Gender,Receiver's Religion,Receiver's Age,Sender's Career,Sender's Gender,Sender's Religion}
    \end{axis}
\end{tikzpicture}

@@

This section briefly discussed our appoaches to ranking the gifts and algorithms with commonsense knowledge base

\subsubsection{Feature Vectors}
As a recommendation system, we use a feature matching type of the recommendation system.
We analyze 60 gifts items and 3 common occasions by 8 features.  
The features are:
1.[ Practical   ] – Is it functional or just for decoration?
2.[ Meaningful  ] – Is it has other meaning besides its function? 
3.[Beautiful    ] – Is it good looking?
4.[Trendy       ] – Is it fashion?
5.[Impersonal   ] – Is it just for him/her or other people can use it?
6.[Romantic ] – Is it present for love and sweet?
7.[Geeky        ] – Is it electrical?
8.[Fun      ] – Is it let you happy in a pure way?
